Carbonate chemistry at Ny-Ålesund

### 2021-02-23 awipev-CO2.Rmd
Completed availability figures

s1 <- summary(as.factor(d_min$pco2_corr_qf))*100/length(d_min$pco2_corr_qf)
s2 <- summary(as.factor(d_min$sal_fb_qf))*100/length(d_min$sal_fb_qf)
s3 <- summary(as.factor(d_min$sal_insitu_ctd_qf))*100/length(d_min$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d_min$temp_fb_qf))*100/length(d_min$temp_fb_qf)
s5 <- summary(as.factor(d_min$temp_insitu_11m_qf))*100/length(d_min$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d_min, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d_min, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "Not deployed or operated", "Acid flush", "Failed visual inspection")
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <- ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  scale_fill_discrete(labels = labels) + 
  coord_flip() +
  #geom_text(aes(label=round(value, digits = 0)), position = position_stack((hjust = 0.5)), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
ggsave(filename = "figures/availability.png", plot = p, width = 20, units = "cm")
kable(z, digits = 1)

# Monthly distribution of hourly data
d2 <- d_all %>% 
  dplyr::select(datetime, montht, pco2_inst, ph_s_sf_temp_insi)
p <- ggplot(data = d2, aes(x = montht, y = pco2_inst)) +
  geom_bar(stat="identity", width = 0.3) +
  scale_fill_discrete(labels = labels) + 
  labs(x="Month", y="pCO2", title = "") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
p
ggsave(filename = "figures/monthly_availability.png", plot = p, width = 20, units = "cm")
#rm(d_min, d2)
```

>>>>

s1 <- summary(as.factor(d_min$pco2_corr_qf))*100/length(d_min$pco2_corr_qf)
s2 <- summary(as.factor(d_min$sal_fb_qf))*100/length(d_min$sal_fb_qf)
s3 <- summary(as.factor(d_min$sal_insitu_ctd_qf))*100/length(d_min$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d_min$temp_fb_qf))*100/length(d_min$temp_fb_qf)
s5 <- summary(as.factor(d_min$temp_insitu_11m_qf))*100/length(d_min$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d_min, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d_min, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "Not deployed or operated", "Acid flush", "Failed visual inspection")
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p_avail <- ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  scale_fill_discrete(labels = labels) + 
  coord_flip() +
  #geom_text(aes(label=round(value, digits = 0)), position = position_stack((hjust = 0.5)), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
#ggsave(filename = "figures/availability.png", plot = p_avail, width = 15, height = 8, units = "cm")
kable(z, digits = 1)

# Monthly distribution of hourly data
d2 <- d_all %>% 
  dplyr::select(montht, pco2_inst, phINT)
count_pco2_inst_no_NA <- sum(!is.na(d2$pco2_inst)) # total non-NA pCO2 values
count_phINT_no_NA <-  sum(!is.na(d2$phINT)) # total non-NA pH seafet values
# calculate the distribution of non-NA pCO2 and pH values per month
d2_summary <- d2 %>% 
  dplyr::group_by(montht) %>% 
  dplyr::summarise(pco2_pc = round(100 * sum(!is.na(pco2_inst))/count_pco2_inst_no_NA, digits = 1),
                   pH_pc = round(100 * sum(!is.na(phINT))/count_phINT_no_NA, digits = 1)
                   )
# plot the distribution of non-NA pCO2 and pH values per month
d2_summary_long <- d2_summary %>% 
  tidyr::pivot_longer(cols = c(pco2_pc, pH_pc))
p_avail_month <- ggplot(data = d2_summary_long) +
  geom_col(aes(x = montht, y = value, fill = name), position = "dodge", width = 0.75) +
  scale_fill_discrete(name = "", labels = c("pCO2", "pH")) + 
  labs(x="Month", y="Percent of total number of data", title = "") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0.5, unit = "cm"))
#ggsave(filename = "figures/monthly_availability.png", plot = p_avail_month, width = 15, height = 8, units = "cm")

# Combine plots
p <- (p_avail / p_avail_month)
p <- p + plot_annotation(tag_levels = 'A')
p
ggsave(filename = "figures/availability.png", plot = p, width = 20, height = 15, units = "cm")

# deleted uneeded data
rm(d_min, list=ls(pattern="^d2"))
```
